\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}

\definecolor{headgray}{RGB}{85,85,85}
\newcommand{\sep}{\;\textcolor{headgray}{|}\;}

\titleformat{\section}{\large\bfseries}{}{0pt}{}[\vspace{-2pt}\hrule\vspace{4pt}]
\setlist[itemize]{itemsep=2pt,topsep=2pt,leftmargin=*,parsep=0pt}

\begin{document}

\begin{center}
{\LARGE \bfseries Nazmus Shakib Sayom}\\[4pt]
\normalsize
\href{mailto:nsssayom@gmail.com}{nsssayom@gmail.com} \sep
\href{https://github.com/nsssayom}{github.com/nsssayom} \sep
\href{https://www.linkedin.com/in/nsssayom/}{linkedin.com/in/nsssayom} \sep
\href{https://sayom.me/}{sayom.me}
\end{center}

\section*{Summary}
Ph.D. student in Computer Science at the University of Utah. Researching cyber-physical systems security, currently focused on surrogate-based falsification for autonomous systems and safety policy verification for multi-robot systems.

\section*{Education}
\textbf{Ph.D., Computer Science} \hfill Aug 2024 - Present\\
University of Utah \hfill Research Area: Cyber-Physical Systems Security

\textbf{B.Sc., Computer Science \& Engineering} \hfill 2017 - 2020\\
American International University-Bangladesh \hfill Summa Cum Laude, CGPA: 3.96

\section*{Research Experience}
\textbf{Graduate Research Assistant} \hfill Aug 2024 - Present\\
University of Utah, Salt Lake City, USA
\begin{itemize}
  \item Property-guided falsification for CPS control stacks: build property-scoped reductions of control logic and physical dynamics to accelerate violation discovery; validate counterexamples on full systems (e.g., PX4, ArduPilot).
  \item Safety policy verification in multi-robot systems with multiple stakeholders: formalize policies, model role/permission constraints, analyze conflicts, and assess runtime monitoring.
\end{itemize}

\section*{Industry Experience}
\textbf{Linux Developer} \hfill Jan 2023 - Jul 2024\\
meldCX, Dhaka, Bangladesh
\begin{itemize}
  \item Developed application-specific embedded Linux distributions for ARM SoCs/SoMs.
  \item Implemented OS-agnostic, network-accessible abstractions for device drivers to improve performance and maintainability.
\end{itemize}

\textbf{Senior Software Engineer} \hfill Apr 2021 - Dec 2021\\
HelloTask Platform Ltd., Dhaka, Bangladesh
\begin{itemize}
  \item Led design and development of a jobs platform for blue-collar workers.
  \item Built an IVR broadcasting and input-collection system for users without internet access.
\end{itemize}

\textbf{Embedded Systems Engineer} \hfill Jun 2020 - Mar 2021\\
HelloTask Platform Ltd., Dhaka, Bangladesh
\begin{itemize}
  \item Prototyped a self-checkout store network to improve customer experience and security.
  \item Built a centralized out-of-home advertising delivery platform using IoT and computer vision analytics.
\end{itemize}

\textbf{Lecturer (ETE/ICE)} \hfill Jan 2022 - Dec 2022\\
Daffodil International University, Dhaka, Bangladesh
\begin{itemize}
  \item Taught Operating Systems, Embedded Systems, and Computer Fundamentals.
  \item Co-authored two conference papers in deep learning; secured funding for low-cost educational technology research.
\end{itemize}

\section*{Selected Projects}
\textbf{Disaster Victim Tracking} - Multi-layer communications (ESP32, LoRaWAN, BLE, GSM) for resilient search-and-rescue.\\
\textbf{Voice Remote (AOSP TV)} - Arduino + nRF24 with IBM Watson STT.\\
\textbf{Depen} - Raspberry Pi Zero OCR-centric tangible interface.\\
\textbf{TALK-E} - Long-range digital walkie-talkie on nRF24L01+.\\
\textbf{Dancing Bees} - Python/OpenCV visualization of honey-bee trajectories.

\section*{Technical Skills}
\textbf{Languages:} C/C++, Python, JavaScript/TypeScript, Bash \\
\textbf{Frameworks:} Yocto, Node.js, NestJS, FastAPI, PyTorch, TensorFlow \\
\textbf{Tools:} Git, CMake, Docker, OpenCV, SQL, MongoDB, InfluxDB \\
\textbf{Protocols:} UART, I2C, SPI, LoRaWAN, BLE, REST, MQTT, WebSocket, GraphQL \\
\textbf{Hardware:} Raspberry Pi (3/4/CM4), ESP32, STM32, Toradex Verdin i.MX8M Mini, Firefly Core-3566JD4, Arduino

\section*{Honors \& Awards}
Summa Cum Laude (AIUB); Dean's List (Spring and Fall 2019); Champion, App Development, AIUB CS Fest 2017.

\end{document}
